---
title: "R Notebook"
output: html_notebook
---

1. Load the necessary datafiles (and libraries)

```{r, message=FALSE, warning=FALSE}

library(igraph)
library(dplyr)
library(ggplot2)
library(plotly)

source("custom_functions.R")

version = "specific"
model = "gpt-4-turbo"
temperature_curation = "0-3"
temperature_matching = "0-3"

meta = read.csv("../data/raw/team_meta.csv", stringsAsFactors = FALSE)
roster = read.csv("../data/raw/teams_info_members_db.tsv", sep = "\t", stringsAsFactors = FALSE)
roster$edited_name = trimws((iconv(roster$UserName,from="UTF-8",to="ASCII//TRANSLIT")))


```


Load Manual Curation

```{r}

manual = read.csv("../data/processed/manually_curated/random_per_year_intra_team/intra-team_manual_annotated_new.csv", stringsAsFactors = FALSE)[,c("Year", "Team", "UserName", "MemberType", "activities", "category")]

manual$category = lapply(manual$category, FUN = function(x) trimws(strsplit(x, ",")[[1]])) 
manual$UserName = trimws((iconv(manual$UserName,from="UTF-8",to="ASCII//TRANSLIT")))

manual = tidyr::unnest(manual, cols = "category")
manual$activities = tolower(manual$activities)

```

Load for specified models

```{r}

model = "gpt-4-turbo"

df = read.csv(paste("../data/processed/gpt_curated/intra-team/intra-team_merged_", version, "_", model, "_", temperature_matching, "_", temperature_curation, ".csv", sep = ""), stringsAsFactors = FALSE)
  
```

Create the Networks (GPT)

```{r}

g_list_gpt = list()

for (year in unique(df$year))
{
  temp_list = list()
  
  for (team in unique(df$team[df$year == year]))
  {
    t = df[df$in_gpt == TRUE & df$team == team & df$year == year,]
    
    v = roster[roster$Team == team & roster$Year == year, c("edited_name", "MemberType")]
    v$type = TRUE
    colnames(v) = c("name", "role_type", "type")
    v = v[!duplicated(v),]
    
    v = rbind(v, data.frame(name = unique(t$category), role_type = "activity", type = FALSE))
    
    v$year = year
    v$team = team
    
    g_gpt = graph_from_data_frame(t[,c("member", "category")], vertices = v, directed = FALSE)
    
    temp_list[[team]] = g_gpt
  }
  
  g_list_gpt[[as.character(year)]] = temp_list
}

```

Create the Networks (Manual)

```{r}

g_list_manual = list()

for (year in unique(df$year))
{
  temp_list = list()
  
  for (team in unique(df$team[df$year == year]))
  {
    t = df[df$in_manual == TRUE & df$team == team & df$year == year,]
    
    v = roster[roster$Team == team & roster$Year == year, c("edited_name", "MemberType")]
    v$type = TRUE
    colnames(v) = c("name", "role_type", "type")
    v = v[!duplicated(v),]
    
    v = rbind(v, data.frame(name = unique(t$category), role_type = "activity", type = FALSE))
    
    v$year = year
    v$team = team
    
    g_manual = graph_from_data_frame(t[,c("member", "category")], vertices = v, directed = FALSE)
    
    temp_list[[team]] = g_manual
  }
  
  g_list_manual[[as.character(year)]] = temp_list
}

```


Plot of Degree Distributions

```{r}

ddist_users = data.frame()
ddist_pages = data.frame()

degree_gpt = data.frame()
degree_manual = data.frame()

for (year in as.character(unique(df$year)))
{

  for (team in names(g_list_gpt[[(year)]]))
  {
    g_gpt = g_list_gpt[[(year)]][[team]]
    g_manual = g_list_manual[[(year)]][[team]]
    
    d_u = degree_distribution(g_gpt, v = V(g_gpt)[V(g_gpt)$type == TRUE], cumulative = TRUE)
    d_p = degree_distribution(g_gpt, v = V(g_gpt)[V(g_gpt)$type == FALSE], cumulative = TRUE)
    
    ddist_users = rbind(ddist_users, data.frame(team = team, value = d_u, id = 0:(length(d_u)-1), year = year, type = "gpt")) 
    
    ddist_pages = rbind(ddist_pages, data.frame(team = team, value = d_p, id = 0:(length(d_p)-1), year = year, type = "gpt"))
    
    d_u = degree_distribution(g_manual, v = V(g_manual)[V(g_manual)$type == TRUE], cumulative = TRUE)
    d_p = degree_distribution(g_manual, v = V(g_manual)[V(g_manual)$type == FALSE], cumulative = TRUE)
    
    ddist_users = rbind(ddist_users, data.frame(team = team, value = d_u, id = 0:(length(d_u)-1), year = year, type = "manual"))  
    ddist_pages = rbind(ddist_pages, data.frame(team = team, value = d_p, id = 0:(length(d_p)-1), year = year, type = "manual"))
    
    degree_gpt = rbind(degree_gpt, data.frame(team = team, year = year, vertices = V(g_gpt)$name, degree_gpt = degree(g_gpt), type = V(g_gpt)$type))
    
    degree_manual = rbind(degree_manual, data.frame(team = team, year = year, vertices = V(g_manual)$name, degree_manual = degree(g_manual), type = V(g_manual)$type))
    
    
  }
}

```

Correlations (degree)

```{r}

deg = merge(degree_gpt, degree_manual, by.x = c("team", "year", "vertices", "type"), by.y = c("team", "year", "vertices", "type"), all.x = TRUE, all.y = TRUE)

deg[is.na(deg)] = 0

```


Plot (Users)

```{r}

vir = viridis::viridis(6)
color_palette = c("grey", vir[2:6])

ddist_users$identifier = paste(ddist_users$team, ddist_users$year, sep = "-")

ddist_pages$identifier = paste(ddist_pages$team, ddist_pages$year, sep = "-")

plt = ggplot() + geom_line(data = ddist_users[ddist_users$type == "gpt",], aes(x = log(id, base = 10), y = log(value, base = 10), group = identifier), alpha = 0.3, color = color_palette[5])  + theme_bw(base_size = 15) + geom_line(data = ddist_users[ddist_users$type == "manual",], aes(x = log(id, base = 10), y = log(value, base = 10), group = identifier), alpha = 0.3, color = "lightgrey") + 
```

Plot (Pages)

```{r}


plt = ggplot() + geom_line(data = ddist_pages[ddist_pages$type == "gpt",], aes(x = log(id, base = 10), y = log(value, base = 10), group = identifier), alpha = 0.3, color = color_palette[5])  + theme_bw(base_size = 15) + geom_line(data = ddist_pages[ddist_pages$type == "manual",], aes(x = log(id, base = 10), y = log(value, base = 10), group = identifier), alpha = 0.3, color = "lightgrey")

```

Average Plot

```{r}

users = ddist_users %>% group_by(id, type) %>% summarise(mean = mean(log(value, base = 10)), se = se(log(value, base = 10)))
users$side = "users"

pages = ddist_pages %>% group_by(id, type) %>% summarise(mean = mean(log(value, base = 10)), se = se(log(value, base = 10)))
pages$side = "pages"

t = rbind(users, pages)
t$identifier = paste(t$type, t$side, sep = "-")

plt = ggplot(t) + geom_line(aes(x = log(id, base = 10), y = mean, color = type)) + geom_errorbar(aes(ymin = mean-se, ymax = mean+se, x = log(id, base = 10), color = type)) + theme_bw(base_size = 25) + scale_color_manual(breaks = c("gpt", "manual"), values = c(color_palette[5], "grey")) + xlab("") + ylab("") + theme(panel.grid.major = element_blank(),
panel.grid.minor = element_blank()) + theme(legend.position="none") + facet_wrap(~side)


ggsave(plt, filename = "../figures/intra-team_cumulative_deg_dist.png", width = 10, height = 7)

#plt = ggplot() + geom_line(data = users, aes(x = log(id, base = 10), y = mean, fill = type), alpha = 1) + geom_errorbar(data = users, aes(ymin = mean-se, ymax = mean+se, x = log(id, base = 10), fill = type), width = 0.0) + theme_bw(base_size = 15) + geom_line(data = pages, aes(x = log(id, base = 10), y = mean, fill = type), alpha = 1)  + geom_errorbar(data = pages, aes(ymin = mean-se, ymax = mean+se, x = log(id, base = 10), fill = type), width = 0.0) + scale_fill_manual(breaks = c("gpt", "manual"), values = (color_palette[c(4,5)])) + xlab("") + ylab("")

```


Compute Nestedness & Modularity

```{r, warning=FALSE, message=FALSE}

library(maxnodf)

df_nestedness = data.frame()

for (year in names(g_list_gpt))
{
 
  for (team in names(g_list_gpt[[year]]))
  {
    g = g_list_gpt[[year]][[team]]
    #Remove isolates
    d = degree(g)
    g = induced_subgraph(g, vids = names(d[d>0]))
    web_gpt = as_incidence_matrix(g, sparse = FALSE)
    
    g = g_list_manual[[year]][[team]]
    #Remove isolates
    d = degree(g)
    g = induced_subgraph(g, vids = names(d[d>0]))
    web_manual = as_incidence_matrix(g, sparse = FALSE)
    
    df_nestedness = rbind(df_nestedness, data.frame(team = team, year = year, type = "gpt", nodfc = NODFc(web_gpt), modularity = rnetcarto::netcarto(t(web_gpt), bipartite = TRUE)[[2]]))
    
    df_nestedness = rbind(df_nestedness, data.frame(team = team, year = year, type = "manual", nodfc = NODFc(web_manual), modularity = rnetcarto::netcarto(t(web_manual), bipartite = TRUE)[[2]]))
    
  }
   
}

```

Plot nestedness v modularity

```{r}


temp = reshape2::dcast(df_nestedness, formula = team+year~type, value.var = "nodfc")

plt = ggplot(temp, aes(x = manual, y = gpt)) + theme_bw(base_size = 25) + geom_point(alpha = 0.5)  + geom_abline(linetype = "dashed", color = "black", alpha = 0.5) + xlab("") + ylab("") + theme(panel.grid.major = element_blank(),
panel.grid.minor = element_blank()) + theme(legend.position="none")


ggsave(plt, filename = "../figures/nestedness_intra-team.png", height = 5, width = 5)

#temp = reshape2::dcast(df_nestedness, formula = team+year~type, value.var = "modularity")

#plt = ggplot(temp, aes(x = manual, y = gpt)) + theme_bw(base_size = 25) + geom_point()  + geom_abline(linetype = "dashed", color = "red")


```


Plot Incidence Matrices with the Nested Alignment

```{r}

#Function - make the alignment of the incidence matrix which maximises nestedness

plot_heatmap = function(g)
{
  #g = graph
  df = as_incidence_matrix(g)
  
  a = bipartite::nestedrank(df)
  
  df = as.data.frame(df)
  
  if (ncol(df) == 1 | nrow(df) == 1)
    return(0)
      
  df = df[,c(names(sort(a$`higher level`, decreasing = TRUE)))]
  df = df[c(names(sort(a$`lower level`, decreasing = FALSE))),]
  
        #colnames(df) = paste(1:ncol(df), "-m", sep = "")
  #rownames(df) = paste(1:nrow(df), "-n", sep = "")
  
  df_melt = reshape2::melt(as.matrix(df))
  colnames(df_melt) = c("page", "user", "edge")
  
  plt = ggplot(df_melt, aes(x = page, y = user, fill = edge)) + geom_tile(lwd = 1.5, linetype = 1) 
  plt = plt + scale_fill_gradientn(colors = c("white", "red")) + theme_bw(base_size = 15) + xlab("Page") + ylab("")
  plt = plt + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
  
  return(plt)
}


```

Network Heatmaps

```{r}

pdf("../figures/network_heatmaps.pdf", height = 7, width = 15)

for (year in names(g_list_gpt))
{
 
  for (team in names(g_list_gpt[[year]]))
  {
    g_gpt = g_list_gpt[[year]][[team]]
    g_manual = g_list_manual[[year]][[team]]
    
    plt_gpt = plot_heatmap(g_gpt) + ggtitle("GPT")
    plt_manual = plot_heatmap(g_manual) + ggtitle("Manual")
    
    print(ggpubr::ggarrange(plt_gpt, plt_manual))
    
  }
  
}

dev.off()
```
